Improving Estimates of the State of Global Fisheries <br> Depends on Better Data

### 2021-06-17 documents/ovando-etal-assessing-global-fisheries.Rmd
fixed new FAO areas mapping problem

assess_ram_fits <- read_rds(path = file.path(results_path,"assess_ram_fits.rds"))

ram_v_sraplus_area <- read_rds(path = file.path(results_path,"ram_v_sraplus_area.rds"))

ram_comp_data <- read_rds(path = file.path(results_path,"ram_comp_data.rds"))

fao_sraplus_comp_data <- read_rds(path = file.path(results_path, "fao_sraplus_comp_data.rds"))

@@

  exs <- read_rds(path = file.path(results_path, "raw-case-study-fits.rds"))

>>>>

assess_ram_fits <- read_rds(file = file.path(results_path,"assess_ram_fits.rds"))

ram_v_sraplus_area <- read_rds(file = file.path(results_path,"ram_v_sraplus_area.rds"))

ram_comp_data <- read_rds(file = file.path(results_path,"ram_comp_data.rds"))

fao_sraplus_comp_data <- read_rds(file = file.path(results_path, "fao_sraplus_comp_data.rds"))

@@

  exs <- read_rds(file = file.path(results_path, "raw-case-study-fits.rds"))
